Precision calculations of the cosmic shear power spectrum projection

### 2017-07-17 limber2.tex
Patrick/Marika's comments; removed ref to Kitching v1 in abstract

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations \forref{is} negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by Kitching et al. (2016, version 1)

@@

The outlier in the flat-sky cases is the extended Limber approximation
(ExtL1Fl) which performs relatively poorly, and reaches 10\% precision only at
$\ell > 100$. The same slow convergence can be observed for the corresponding
second-order flat case, ExtL2Fl. To our knowledge this form of the flat-sky
approximation has not been used in any cosmic shear studies to date, and should
not be used in any future studies given these results.  The poor behaviour of
this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be
understood by considering Taylor expansions of the different pre-factors.  The
spherical pre-factor,
%
\begin{equation}
p(\ell) = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, ,
\end{equation}
%
can be compared to the flat-sky extended Limber pre-factor
%
\begin{equation}
p(\ell) = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
\end{equation} 
%
showing it to be more deviant from the full spherical solution, than the
`hybrid' $p(\ell) = 1$ case.

@@

\forref{
The calculation of the shear correlation function on the sphere requires the
estimation of the reduced Wigner ${\rm D}$-matrices ${\rm d}^\ell_{22}$ and
${\rm d}^\ell_{2-2}$. The general calculation of ${\rm d}^\ell_{m\,n}$ is
cumbersome, but there are quick and numerically stable recurrence relations if
we are interested in only a subset of these matrices. In particular, following
\citet{BLANCO199719} we can show that
%
\begin{equation}
%
{\rm d}^\ell_{m\,n}={\ell(2\ell-1)\over \sqrt{[\ell^2-m^2][\ell^2-n^2]}}
%
\left[ \left( {\rm d}^1_{00}-{mn\over \ell(\ell-1)} \right) {\rm d}^{\ell-1}_{mn}
%
-{\sqrt{[(\ell-1)^2-m^2][(\ell-1)^2-n^2]}\over (\ell-1)(2\ell-1)} {\rm d}^{\ell-2}_{mn}\right] ,
%
\end{equation}
%
which allows to calculate all required reduced Wigner ${\rm D}$-matrices from the first two elements.
}

>>>>

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations \forref{is} negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated.
%, in
%contrast to the recent claim made by Kitching et al. (2016, version 1)

@@

The outlier in the flat-sky cases is the extended Limber approximation
(ExtL1Fl) which performs relatively poorly, and reaches 10\% precision only at
$\ell > 100$. The same slow convergence can be observed for the corresponding
second-order flat case, ExtL2Fl. To our knowledge this form of the flat-sky
approximation has not been used in any cosmic shear studies to date, and should
not be used in any future studies given these results.  The poor behaviour of
this case, in comparison with the `hybrid' case, (e.g.~ExtL1FlHyb) can be
understood by considering Taylor expansions of the different pre-factors.  The
spherical pre-factor,
%
\begin{equation}
p(\ell) = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, ,
\end{equation}
%
can be compared to the flat-sky extended Limber pre-factor
%
\begin{equation}
p(\ell) = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
\end{equation} 
%
showing it to be more deviant from the full spherical solution, than the
`hybrid' $p(\ell) = 1$ case.

@@

\forref{
The calculation of the shear correlation function on the sphere requires the
estimation of the reduced Wigner ${\rm D}$-matrices ${\rm d}^\ell_{2\,2}$ and
${\rm d}^\ell_{2\,-2}$. The general calculation of ${\rm d}^\ell_{m\,n}$ is
cumbersome, but there are quick and numerically stable recurrence relations if
we are interested in only a subset of these matrices. In particular, following
\citet{BLANCO199719} we can show that
%
\begin{equation}
%
{\rm d}^\ell_{m\,n}={\ell(2\ell-1)\over \sqrt{[\ell^2-m^2][\ell^2-n^2]}}
%
\left[ \left( {\rm d}^1_{0\,0}-{m\,n\over \ell(\ell-1)} \right) {\rm d}^{\ell-1}_{m\,n}
%
-{\sqrt{[(\ell-1)^2-m^2][(\ell-1)^2-n^2]}\over (\ell-1)(2\ell-1)} {\rm d}^{\ell-2}_{m\,n}\right] ,
%
\end{equation}
%
which allows to calculate all required reduced Wigner ${\rm D}$-matrices from the first two elements.
}
